Lens Modeling in \sw

### 2014-01-20 text/ms.tex
only reformatting orginial changes

\usepackage{amsmath}
\usepackage{xspace}   % fixes spaces after custom commands
\usepackage{float}    % exact placement of figures (using \begin{figure}[H])
\usepackage{color}  % well... color...
\usepackage{setspace}    % remove this pgk for final compile!! 
\usepackage{subfigure}

\usepackage{longtable}   % those two to generate the 2 ol table
\usepackage{multicol}

@@

% shortcut for ASW000xxxx
\newcommand{\asw}[1]{ASW000#1\xspace}

\newcommand{\model}[2][Model~]{#1#2\xspace}

@@

% todo annotations on side in red. easy to search for at the end
\newcommand{\todo}[2][red]{%\marginpar{\raggedright\scriptsize\sffamily\textcolor{red}{#1}}}

\textcolor{#1}{\textbullet}%
\marginpar{\colorbox{#1}{\parbox{\marginparwidth}{%
\setstretch{0.4}\sffamily\textcolor{black}{\scriptsize{#2}}}}}}

@@

@@

\begin{abstract}
In the initial phase of Spacewarps (SW1), volunteers were invited to search the CFHTLS sky survey to look for gravitational lenses. Here we report on a web interface    
that gives experienced volunteers the opportunity to model the candidates that have been identified. These volunteers, were also invited to model a sample of 29 simulated lenses, to order to gauge the quality of the models that were being generated. These were then examined in greater detail, with particular attention being paid to the following: (i)~identification of image parities and time arrivals; (ii)~the mean convergence (equivalent to the enclosed mass), and finally;
 (iii)~ the performance of a volunteer vs. a professional. In most cases, the volunteers were found to correctly identify the image parities and time arrivals, along with a mean convergence that was contained within the image region; In all, the results could be comparable to that of professionals.

\todo[red]{or should that be web application? Also, I change the tense of the opening statement. Not too sure of the correct way of introducing an abbreviation (SW1 in this case), and I was a bit liberal with my editing - Sorry. Another comment - is 'Well contained' better than 'contained' or is it just a figure of speech?}

>>>>

\usepackage{amsmath}
\usepackage{xspace}     % fixes spaces after custom commands
\usepackage{float}      % exact placement of figures (using \begin{figure}[H])
\usepackage{subfigure}  % does what it says

%\usepackage{longtable}   % those two to generate the 2 ol table
%\usepackage{multicol}

@@

% shortcut for ASW000xxxx
\newcommand{\asw}[1]{ASW000#1\xspace}
\newcommand{\model}[2][Model~]{#1#2\xspace}

@@

% todo annotations on side in red. easy to search for at the end
% !!! REMOVE THIS LINES FOR FINAL COMPILE
%
\usepackage{setspace}    % remove this pgk for final compile!! 
\usepackage{color}    % well... color...

\newcommand{\todo}[2][red]{%
\textcolor{#1}{\textbullet}%
\marginpar{\colorbox{#1}{\parbox{\marginparwidth}{%
\setstretch{0.4}\sffamily\textcolor{black}{\scriptsize{#2}}}}}}

@@

% \\\ END OF REMOVAL SECION

@@

\begin{abstract}
In the initial phase of Spacewarps (SW1), volunteers were invited to search the CFHTLS sky survey to look for gravitational lenses.
Here we report on a web interface that gives experienced volunteers the opportunity to model the candidates that have been identified.
These volunteers, were also invited to model a sample of 29 simulated lenses, to order to gauge the quality of the models that were being generated.
These were then examined in greater detail, with particular attention being paid to the following:
(i)~identification of image parities and time arrivals;
(ii)~the mean convergence (equivalent to the enclosed mass), and finally;
(iii)~the performance of a volunteer vs. a professional.
In most cases, the volunteers were found to correctly identify the image parities and time arrivals, along with a mean convergence that was contained within the image region;
In all, the results could be comparable to that of professionals.

\todo{see code}
% or should that be web application?
% Also, I change the tense of the opening statement.
% Not too sure of the correct way of introducing an abbreviation (SW1 in this case), and I was a bit liberal with my editing - Sorry.
% Another comment - is 'Well contained' better than 'contained' or is it just a figure of speech?}
